---
title       : Affect on Miles Per Gallon
subtitle    : Course Project
author      : Rashid Chohan
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

We'll examine the factors which can affect efficiency of cars (in terms of Miles Per Gallon).

The data is from Motor Trend Magazine and was published in 1974

--- .class #id 

This is how the data looks like

```{r echo=FALSE}
library(datasets)

library(slidify)

mydat = data(mtcars)

fit = lm(mpg ~ .)  
summary(fit)  


```


--- .class #id 
Summary of data

'''{r echo=FALSE}

plot(data=mydat, mtcars, xlab = "Factors", ylab = "MPG")


```



--- .class #id 

```{r echo=FALSE}
plot(data=mydat, mtcars, xlab = "Factors", ylab = "MPG")

```

--- .class #id 
Affect of several factors on MPG

```{r echo=FALSE}
plot(data=mydat, mtcars, xlab = "Factors", ylab = "MPG")


```
